---
title: "Intermediate Elective"
author: "Kelsey Hammond"
date: "05-22-2026"
format: pdf
---
# Problems
## 1. Explain your inspiration

I chose Cédric Scherer’s “Bill Dimensions of Brush-tailed Penguins”. This visualization makes sense for my dataset because I am exploring the relationship between waterfowl species abundance and water salinity and they are both quantitative variables. The x-axis will be salinity and the y-axis will be waterfowl abundance.

## 2. Plan your figure

## 3. Code your figure
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, fig.showtext = T, fig.retina = 1)
```

```{r prep, message=FALSE}
## packages
library(tidyverse)
library(colorspace)
library(ragg)
library(cowplot)
library(ggtext)
library(pdftools)

theme_set(theme_minimal(base_size = 15, base_family = "Neutraface Slab Display TT Bold"))

theme_update(
  panel.grid.major = element_line(color = "grey92", size = .4),
  panel.grid.minor = element_blank(),
  axis.title.x = element_text(color = "grey30", margin = margin(t = 7)),
  axis.title.y = element_text(color = "grey30", margin = margin(r = 7)),
  axis.text = element_text(color = "grey50"),
  axis.ticks =  element_line(color = "grey92", size = .4),
  axis.ticks.length = unit(.6, "lines"),
  legend.position = "top",
  plot.title = element_text(hjust = 0, color = "black", 
                            family = "Neutraface 2 Display Titling",
                            size = 21, margin = margin(t = 10, b = 35)),
  plot.subtitle = element_text(hjust = 0, face = "bold", color = "grey30",
                               family = "Neutraface Text Book Italic", 
                               size = 14, margin = margin(0, 0, 25, 0)),
  plot.title.position = "plot",
  plot.caption = element_text(color = "grey50", size = 10, hjust = 1,
                              family = "Neutraface Display Medium", 
                              lineheight = 1.05, margin = margin(30, 0, 0, 0)),
  plot.caption.position = "plot", 
  plot.margin = margin(rep(20, 4))
)

pal <- c("#FF8C00", "#A034F0", "#159090")
```

```{r}
#| label: data

water_quality <- read.csv(here("data", "YSI_Data_Begin_1.csv"))
birds <- read.csv(here("data", "birds.csv")) |> filter(e_bird_group %in% c("Waterfowl", "Shorebirds", "Herons, Ibis, and Allies"))
venoco_water <- read.csv(here("data", "venoco-water.csv"))
```

